I am writing to express my enthusiasm for the Research Scientist position in Robotics at Google DeepMind in Mountain View. 
My PhD at the University of Toronto is in its final stages, and my defense will be completed by April 2025. 
I have a strong background in robotic imitation learning, inverse reinforcement learning, and addressing distribution shift, and I am eager to contribute to DeepMind’s mission of building “Embodied AI” to improve lives through advanced robotic capabilities.

During my doctoral studies under Dr. Jonathan Kelly, I have focused on addressing distribution shift in robotic imitation learning, culminating in multiple high-impact publications. 
My recent work, "Efficient Imitation Without Demonstrations via Value-Penalized Auxiliary Control from Examples" (ICRA 2025 submission), built directly on previous work from Deepmind (SAC-X) and was \href{https://x.com/m_wulfmeier/status/1864709951823675882}{tweeted by Markus Wulfmeier}. 
I explored novel approaches to improve robot inverse reinforcement learning via auxiliary tasks and simpler example-based datatsets, which is one way we could circumvent the suboptimality of gigantic human datasets. 
This aligns closely with DeepMind’s commitment to advancing robotic intelligence using large datasets and deep neural networks.

Beyond research, I bring hands-on experience with both simulators and real-world robotic systems. 
My collaborations have spanned multimodal sensor integration, tactile robotics, and reinforcement learning, exemplified by my contribution to "Multimodal and Force-Matched Imitation Learning with a See-Through Visuotactile Sensor" (IEEE Transactions on Robotics, 2024). 
These projects underscore my ability to bridge theoretical advancements with practical implementations, fostering impactful results in embodied AI.

At DeepMind, I am particularly excited about the opportunity to:
\begin{itemize}
    \item Design and evaluate models for robotic agents that transform language instructions into meaningful physical actions.
    \item Collaborate with interdisciplinary teams to tackle ambitious research goals in robotics with some of the best artificial intelligence researchers in the world.
    \item Contribute to the broader mission of creating AI systems that positively impact billions of lives.
\end{itemize}

My passion for advancing robotics is matched by a commitment to collaboration and innovation. I thrive in dynamic environments where I can engage with diverse perspectives to solve complex challenges. With a strong publication record, practical expertise, and a genuine enthusiasm for real-world AI applications, I am confident in my ability to contribute meaningfully to DeepMind’s Robotics team.
Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experiences align with your needs. Please find my CV attached, and I look forward to the possibility of joining your team.
